Machine Learning Models for the Segmentation of eCoaching Text

### 2018-03-02 paper-amia-2018/manuscript.tex
fixed bug in rnn model

 Naive Bayes Multinomial & 0.594 & 0.662 & 0.626 & 0.590 & 0.666 & 0.626 \\ \hline
 Support Vector Machine & 0.742 & \textbf{0.679} & 0.709 & 0.774 & 0.696 & 0.733\\ \hline
 K-Nearest Neighbour & \textbf{0.808} & 0.663 & \textbf{0.728} & \textbf{0.820} & \textbf{0.742} & \textbf{0.779}\\ \hline
 Long Short Term Memory & 0.8424 & 0.8385 & 0.8381 & 0.8424 & 0.8385 & 0.8381\\ \hline
 Gated Recurrent Unit & 0.8705 & 0.8676 & 0.8673 & 0.8412 & 0.8377 & 0.8373\\ \hline 
  \end{tabular}
\end{table}

@@

 Naive Bayes Multinomial & 0.988 & 0.985 & 0.987 & 0.989 & 0.984 & 0.986 \\ \hline
 Support Vector Machine & \textbf{0.989} & 0.992 & 0.991 & 0.990 & 0.993 & 0.991\\ \hline
 K-Nearest Neighbour & \textbf{0.989} & \textbf{0.995} & \textbf{0.992} & \textbf{0.991} & \textbf{0.994} & \textbf{0.993}\\ \hline
 Long Short Term Memory & 0.8424 & 0.8385 & 0.8381 & 0.8424 & 0.8385 & 0.8381\\ \hline
 Gated Recurrent Unit & 0.8705 & 0.8676 & 0.8673 & 0.8412 & 0.8377 & 0.8373\\ \hline 
  \end{tabular}
\end{table}

@@

\section*{Conclusion}
In this paper, we compared the performance of machine learning models for the task of segmentation of e-coaching text. We found out that k-nearest neighbour provides the best performance for the segmentaion of text in terms of all performance metrics. Manual segmentation of e-coaching data is very resource-intensive and time consuming task, which can significantly decrease the time and effort required to develop effective behavioral interventions. Our
proposed methods can help to identify individual text segments, which can be annotated directly with a classification model and increase the effectiveness of behavioral interventions. This approach will help for developing fully automated eCoaching and also accelerate the pace of identifying effective communication strategies linked to healthy eating.

1) The hypothesis and the evidence for and against it are briefly restated \\
2) The original motivation is recapitulated \\
3) The state of the field in the light of this new contribution is reassessed \\
4) describes future research and new directions suggested by the contribution\\
5) in particular, research that would improve the evidence for or against the hypothesis

>>>>

 Naive Bayes Multinomial & 0.594 & 0.662 & 0.626 & 0.590 & 0.666 & 0.626 \\ \hline
 Support Vector Machine & 0.742 & \textbf{0.679} & 0.709 & 0.774 & 0.696 & 0.733\\ \hline
 K-Nearest Neighbour & \textbf{0.808} & 0.663 & \textbf{0.728} & \textbf{0.820} & \textbf{0.742} & \textbf{0.779}\\ \hline
 Long Short Term Memory & 0.8424 & 0.8385 & 0.8381  & -- & -- & --\\ \hline
 Gated Recurrent Unit & 0.8705 & 0.8676 & 0.8673 & -- & -- & --\\ \hline 
  \end{tabular}
\end{table}

 Naive Bayes Multinomial & 0.988 & 0.985 & 0.987 & 0.989 & 0.984 & 0.986 \\ \hline
 Support Vector Machine & \textbf{0.989} & 0.992 & 0.991 & 0.990 & 0.993 & 0.991\\ \hline
 K-Nearest Neighbour & \textbf{0.989} & \textbf{0.995} & \textbf{0.992} & \textbf{0.991} & \textbf{0.994} & \textbf{0.993}\\ \hline
 Long Short Term Memory & 0.8424 & 0.8385 & 0.8381 & -- & -- & --\\ \hline
 Gated Recurrent Unit & 0.8705 & 0.8676 & 0.8673 & -- & -- & --\\ \hline 
  \end{tabular}
\end{table}

@@

\begin{table}[ht]
\centering
\caption{Performance of NB, SVM, KNN, and RNN for the identification of segmentation and continuous eCoaching text. The highest value for each performance metric is highlighted in bold.}
\label{tab:result_under_over_sampled}
  \begin{tabular}{|l|l|l|l|l|l|l|}
  \hline
   \multirow{2}{*}{\textbf{Method}} & \multicolumn{3}{|c|}{\textbf{contextual features only}} & \multicolumn{3}{|c|}{\textbf{contextual + topics + punctuation marks}} \\\cline{2-7}
   & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-Score} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-Score}\\ \hline

 Naive Bayes Multinomial & 0.975 & 0.974 & 0.975 & 0.976 & 0.974 & 0.975 \\ \hline
 Support Vector Machine & 0.981 & 0.982 & 0.981 & 0.983 & 0.983 & 0.983\\ \hline
 K-Nearest Neighbour & \textbf{0.983} & \textbf{0.984} & \textbf{0.983} & \textbf{0.986} & \textbf{0.986} & \textbf{0.986}\\ \hline
 Long Short Term Memory & 0.8424 & 0.8385 & 0.8381 & -- & -- & --\\ \hline
 Gated Recurrent Unit & 0.8705 & 0.8676 & 0.8673 & -- & -- & --\\ \hline 
  \end{tabular}
\end{table}

@@

\section*{Conclusion}
Segmentation of eCoaching text is an integral part of developing an automated eCoaching intervention. Although several studies have done for the segmentation of clinical text into sections and sentences, none of them are used for the segmentation of text into a group of MI behavior in the setting of discourse analysis with email under the principle of motivational interviews. In this paper, we compared the performance of machine learning models for the task of segmentation of e-coaching text. We found out that k-nearest neighbour provides the best performance for the segmentaion of text in terms of all performance metrics. Manual segmentation of e-coaching data is very resource-intensive and time consuming task, which can significantly decrease the time and effort required to develop effective behavioral interventions. Our proposed methods can help to identify individual text segments, which can be annotated directly with a classification model and increase the effectiveness of behavioral interventions. This approach will help for developing fully automated eCoaching and also accelerate the pace of identifying effective communication strategies linked to healthy eating. As our future work, we plan to evaluate our approach on other datasets involves in discourse analysis for enhancing our proposed method.
